{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex
Added picture of NIR spectroscope in Appendix

	\subsection{Near-infrared (NIR) Spectroscopy}
	NIR- spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm). It, therefore, measures the absorption and interaction of this spectrum of radiation with the sample. NIR-spectroscopy is not only faster and cheaper than the standard test procedure – another significant advantage is that it does not need a reagent and thus does not destroy the sample. It is used for analysis in different sectors and fields, like the agrochemical industry and healthcare. Its non-invasive nature makes it also an asset for medical applications like the monitoring of diabetes in which NIR-spectroscopy can detect the worsening of the blood glucose metabolic dysfunction (cf . \cite{FR_li_et_al_2020}). In the context of this paper, the gasoline dataset which is used for the simulation and the application is constructed using NIR spectroscopy. According to \cite{Bohacs_Ovadi_Salgo1998} NIR-spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules). While this paper focuses on the prediction of the octane number of gasoline, other research focuses  on different properties of gasoline such as the olefin, naphtaenic and aromatic content (Parisi et al. 1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characteristics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})

>>>>

	\subsection{Near-infrared (NIR) Spectroscopy}
	NIR- spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm). It, therefore, measures the absorption and interaction of this spectrum of radiation with the sample. NIR-spectroscopy is not only faster and cheaper than the standard test procedure – another significant advantage is that it does not need a reagent and thus does not destroy the sample. It is used for analysis in different sectors and fields, like the agrochemical industry and healthcare. Its non-invasive nature makes it also an asset for medical applications like the monitoring of diabetes in which NIR-spectroscopy can detect the worsening of the blood glucose metabolic dysfunction (cf . \cite{FR_li_et_al_2020}). \\
	In the context of this paper, the gasoline dataset which is used for the simulation and the application is constructed using NIR spectroscopy. According to \cite{Bohacs_Ovadi_Salgo1998} NIR-spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules). While this paper focuses on the prediction of the octane number of gasoline, other research focuses  on different properties of gasoline such as the olefin, naphtaenic and aromatic content (Parisi et al. 1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characteristics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width = \textwidth]{../Graphics/FinderSD.jpg}
			\caption{Finder SD - A Near-Infrared-Spectroscope built by HiperScan GmbH \\
			(source: https://www.hiperscan.com/files/apoident/uploads/Bilder/Neue\_Website/Produkte/FinderSD.jpg)}
		\end{center}
	\end{figure}
